A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-14 paper.tex
Cleaned up section 8.

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{preservation-integration.eps}
\caption{Preservation Integration of Multiple Programs}
\label{fig:Preservation integration}
\end{figure}

@@

{\bf What is the Granularity of Dependencies?}  Dependencies could be handled
at many different levels of granularity.  In this work, we have shown
how they can be handled at the level of entire repositories or individual files.
Other possible choices might include intermediate-sized software packages
(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in fewer packages,
simpler dependency maps, and more wasted space; smaller granularity results
in complex dependency maps and less wasted space.  A hybrid solution may
be able to combine both by storing large granularity dependencies, but
retain the ability to select sub-items out of objects when efficiency demands it.

{\bf What is the Scope of Reuse?}  We have presented the data preservation
problem as primarily one of accurate reproduction: if a result depends
on running program X, we must be able to run exactly X again.  However,
the goal of scientific reproducibility is rarely limited to running
\emph{precisely} what a predecessor did. Often, the objective is to
change a parameter or a data input in order to see how the result is affected.
To that end, the preservation system must capture enough of the surrounding
material to permit modifications to succeed.  From this perspective,
a larger granularity of preservation is desirable.  A better understanding of
how end users will consume preserved software will help to shape how
software is preserved in the first place.

{\bf How to Detect Dependencies?}  If we allow users to work in uncontrolled
environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
the user's script and extract the repository dependencies.  This is clearly
not a scalable approach.  We then demonstrated an automated method of observing
what individual files are accessed by a program. However, this does
not cover all types of dependencies, particularly those that are networked.
More sophisticated observation techniques could infer higher-level information,
such as the RPM package names of the files accessed, the URLs of remote
repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.

{\bf Keep Source, Binary, or Both?}

>>>>

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{preservation-integration.eps}
\caption{Preserving Multiple Artifacts}
\label{fig:Preservation integration}
\end{figure}

@@

{\bf Granularity of Dependencies.}  Dependencies could be handled
at many different levels of granularity.  In this work, we have shown
how they can be handled at the level of entire repositories or individual files.
Other possible choices might include intermediate-sized software packages
(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in fewer packages,
simpler dependency maps, and more wasted space; smaller granularity results
in complex dependency maps and less wasted space.  A hybrid solution may
be able to combine both by storing large granularity dependencies, but
retain the ability to select sub-items out of objects when efficiency demands it.

{\bf Scope of Reuse.}  We have presented the data preservation
problem as primarily one of accurate reproduction: if a result depends
on running program X, we must be able to run exactly X again.  However,
the goal of scientific reproducibility is rarely limited to running
\emph{precisely} what a predecessor did. Often, the objective is to
change a parameter or a data input in order to see how the result is affected.
To that end, the preservation system must capture enough of the surrounding
material to permit modifications to succeed.  From this perspective,
a larger granularity of preservation is desirable.  A better understanding of
how end users will consume preserved software will help to shape how
software is preserved in the first place.

{\bf Dependency Detection.}  If we allow users to work in uncontrolled
environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
the user's script and extract the repository dependencies.  This is clearly
not a scalable approach.  We then demonstrated an automated method of observing
what individual files are accessed by a program. However, this does
not cover all types of dependencies, particularly those that are networked.
More sophisticated observation techniques could infer higher-level information,
such as the RPM package names of the files accessed, the URLs of remote
repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.

{\bf Source, Binary, or Both?}  A science archive might choose to retain
the source code of an artifact or the binary code that can actually run in a given environment.
While conventional wisdom suggests that access to source code is critical for the long term
survival and evolution of a piece of software, it also requires the maintenance of an enormous
amount of supporting software in the form of compilers, linkers, and supporting libraries for
the target platform.  Rebuilding all of these for every invocation of an artifact is
likely to have excessive cost.  We suggest that a realistic repository will have to
maintain \emph{both}: the source describes the ultimate meaning of the code, but
the binary is an important performance cache, a backup if the compiler toolchain should
fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.
